THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-02-17 DishReflectometry/Paper1_v1.tex
added section 5.1.3 and continuing.

\subsubsection{Effect of dish and the feed on delay spectrum estimation}
The delay spectrum of the instrument is the combined response due to the dish and the feed reflections. Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays. Figure \ref{fig:feed_only} shows the delay spectrum of the feed alone while the feed is kept upside down on the ground.  
\subsubsection{Effect of feed height on delay spectrum estimation}
\subsection{Comparison with PAPER antenna}
\section{Comparison with simulations}
\section{Effect of instrument delay spectrum on 21cm power spectrum measurements }

>>>>

\subsubsection{Effect of dish and the feed on delay spectrum estimation}
Measurement equations shows the effects of mutiple reflections of the sky signal between the feed and the dish. Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays. The estimated delay spectrum of the instrument is collectively contributed by all the reflections. We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:freq}. Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no significant multiple reflections in between the feed and the dish. 
 Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays. Figure \ref{fig:feed_only} shows the delay spectrum of the feed alone while the feed is kept upside down on the ground.  
\subsubsection{Effect of feed height on delay spectrum estimation}
\subsection{Comparison with PAPER antenna}
\section{Comparison with simulations}
\section{Effect of instrument delay spectrum on 21cm power spectrum measurements }
